### 2014-02-28 paper/formal.tex
More small fixes.

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that an IFC langauge, |specLang alpha targetLang)|, satisfies non-interference~\tocite{}, without making any reference to properties of |targetLang|.
%
As it turns out, the precise scheduling policy |alpha| dictates
whether or not the guarantee holds for programs with diverging tasks.
For a sequential scheduler, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; with the concurrent schedule,
we can show a stronger result, \emph{termination-sensitive non-interference},
where termination attacks cannot leak information.

>>>>

In this section we present the formal security guarantees provided by
our embedding.
%
Concretely, we show that |specLang alpha targetLang| for an appropriate
scheduler, satisfies non-interference~\tocite{},
without making any reference to properties of |targetLang|.
%
As it turns out, the precise scheduling policy |alpha| dictates
whether or not the guarantee holds for programs with diverging tasks.
For a sequential scheduler, we will only be able to show
\emph{termination-insensitive non-interference}, where a program
may diverge based on secret data; this allows attackers to observe
secrets by observing the termination of tasks.
For the concurrent round-robin schedule,
we can show a stronger result known as
\emph{termination-sensitive non-interference},
where termination attacks cannot leak information.
